\subsection{Meromorphic version on a complex manifold}

For a Riemann surface (meaning, $\dim(X) =1$), the previous result gives us that any finite dimensional reprensentation of $\pi_1(X,x_*)$ can be obtained as the monodromy reprensentation of some linear system of holomorphic differential equations.\\


21st Hilbert problem : given of finite set of points 

\subsubsection{In dimension 1}

\paragraph{Elements of Fuchs theory}

We focus out study around each point of $S$. Without loss of generality, the case around $z=0$ is sufficient.
We will denote $\De$ the disk centered at 0 of radius $\e$ and $\De^*$ the associated punctured disk at $z=0$.

\medskip
If we want to translate the definition of a connection on $\De$, we would say that such a connection is a locally free sheaf of modules $\erond$ over the sheaf of rings of meromorphic function defined on $\De$ with only a pole at $0$, equipped with a map $\nabla : \erond \to \erond \tensor{\holo_{\De}} \Omega^1_{\De}$ with linearity and Liebniz propreties.\\
We can assume that $\erond$ is free. Moreover, it's more convenient to work with the field of germs of meromorphic functions around 0 denoted $K$. \\
Having localised our study, we then won't work with sheaf in this paragraph. We basically follow Haefliger's lecture in \cite{borel_dmodules}, and the theory exposed is usually refered to as the \textit{Fuchs theory}.\\
This shift of persective leads us to the following definition.

\begin{mydef}
A (germ of) \textit{meromorphic connexion} at 0 is a finite dimensional vector space $M$ over $K$ equipped with an operator $\CC$-linear $\nabla : M \to M$ saisfying the Liebniz rule :
\begin{center}
$\d \forall (h,u) \in K \times M : \nabla(hu)  = \frac{dh}{dz}u + h \nabla u$.
\end{center}
\end{mydef}


With this definition, a morphism of connection is of linear morphism commuting with connections.


\begin{myrem}
The ring $D[z^{-1}]$ of germs of differential operators with meromorphic coefficients acts on a meromorphic connection $(M,\nabla)$ by $Pu = \sum_{j=1}^N a_j \nabla^j u$ if $P = \sum_{j=1}^N a_j \frac{d^j}{dz^j}$ and $u\in M$.
\end{myrem}


\begin{myrem}
As explained in \ref{connections_diff_eq}, given a basis of $M$, a connection map on $M$ is equivalent to a system of differential equations : a meromorphic connection is given by $\nabla = d - A dz$, where $A$ is a matrix with coefficient in $K$, and vice versa.\\
A morphism between systems of equation given by matrices $A$ and $B$ respectively is then a matrix $M : \De^* \to M_n(K)$ such that $\frac{dM}{dz} = BM - MA$, and we say that two systems of differential equations are \textit{equivalent} if $M(z)$ is invertible for any $z \in \De$ (or equivalently, the associate connections are isomorphic). \\
In the rest of the paragraph, we will juggle between these two definitions.
\end{myrem}


Let us compute the monodromy associated to a differential system $y' = Ay$ on $\De$.\\
First, recall that the universal cover of $\De^*$ given by the exponential is $\{t\in \CC, |e^{2i \pi t}| < \e\}$. Multi-valued functions are thus defined on this universal cover. $t$ and $\tilde{\cdot}$ will belong to the universal cover and $z$ to $\De$.\\
Let $\tilde{S}(t) = (\tilde{U}_1,\dots,\tilde{U}_n)$ a fundamental system of multi-valued solutions. $A$ is 1-periodic on the universal cover, so $t \mapsto \tilde{S}(t+1)$ is also a solution. This, there exists a constant invertible matrix $C$ such that $\tilde{S}(t+1) = \tilde{S}(t) C$.

\begin{mydef}
The matrix $C$ defined above is called the \textit{monodromy matrix} of the system.
\end{mydef}

To get back in the punctured disk, let $\Gamma$ a matrix such that $C = \exp(2i \pi \Gamma)$. Then, $\tilde{S}(t)\exp(-2i\pi t \Gamma)$ is 1-periodical on the universal cover, and one can well define $\Sigma(z) = \tilde{S}(\frac{1}{2i\pi}\log(z))e^{\log(z)\Gamma}$. Finally, we set $S(z) = \Sigma(z) e^{\log(z) \Gamma}$.


\medskip
One cannot expect to have a correspondence between the category of meromorphic connections and the one of representations of $\pi_1(\De^*)$, as the following example shows :


\begin{myex} \label{pathological_ex_regular_connection}
Define the two connections $\nabla_1 = d$ and $\nabla_2 = d - \frac{dz}{z^2}$. They are not equivalent since $z \mapsto 0$ is not invertible, but they both have the trivial monodromy (the solutions of $\nabla_2$ are of the form $Ce^{-1/z}$).
\end{myex}


This phenomenon can be intuited as resulting of a \textit{bad} behavior of the solutions at $z=0$, meaning that they have there sort of an essential singularity.\\
Thus, we introduce a \textit{nice} class of functions.


\begin{mydef}
Let $f$ be a multivalued function around 0.\\
$f$ has \textit{moderated growth} if, for all sector $S^\eta_{(a,b)} := \{z \in D_\eta^* ~|~ \arg(z) \in (a,b)\}$ over which $f$ is defined, there exist $k \in \NN$ and $C>0$ such that :
\begin{center}
$\d \forall z \in S^\eta_{(a,b)}, ~|f(z)| \leq C|z^{-k}|$.
\end{center}
\end{mydef}


\begin{myex}
\begin{itemize}
\item[1)] If $f$ is a single-valued function, $f$ has moderate growth if, and only if $f$ is meromorphic on $\De$ (for $\e$ small enough).
\item[2)] $z^\alpha$ for $\alpha\in \CC$, $\log(z)^m$ for $m \in \NN$, have moderate growth.
\end{itemize}
\end{myex}


The following result if very powerful : it gives you information on the behavior of the solutions of a differential equation just by checking a condition on the coefficients of the differential operator with a very simple computation.


\begin{mytheo}[Fuchs]
Let $P = \sum_{k=0}^n a_k(z) \frac{d^{n-k}}{dz^{n-k}}$ a differential operator on $\De$ with the $a_k$'s meromorphic.\\
The followings are equivalent :
\begin{itemize}
\item[i)] the solutions of $Pu=0$ have moderate growth,
\item[ii)] for every $1 \leq i \leq n$, $\frac{a_i}{a_0}$ has a pole of order at most $i$ at $0$.
\end{itemize}
\end{mytheo}

These systems are those we are interested in for an expected correspondence.


\begin{mydef}
A differential operator is said to be \textit{regular} if it satifies the conditions of the previous theorem.
\end{mydef}


\begin{myex}
As expected, the example given in \ref{pathological_ex_regular_connection} is not regular.
\end{myex}


\begin{mytheo}
Let $(E) : y' = Ay$ a differential system on $\De$.
The followings are equivalent :
\begin{itemize}
\item[i)] $(E)$ is equivalent to a regular system,
\item[ii)] $(E)$ is equivalent to a system $y' = \frac{B(z)}{z} y$ for some matrix $B$ holomorphic on $\De$,
\item[iii)] $(E)$ is equivalent to a system $y' = \frac{\Gamma}{z}y$ for some constant matrix $\Gamma$.
\end{itemize}
\end{mytheo}

\begin{mydemo}
.
\end{mydemo}

With this theorem, the equivalent definition in terms of connections is the following :

\begin{mydef}
Let $(M,\nabla)$ be a meromorphic connection.\\
It is said to e an \textit{regular connection} if there exists a basis $\tuple{e}{n}$ of $M$ over $K$ and holomorphic functions $(b_{i,j}(z))$ such that :
\begin{center}
$\d \forall i \in \llbracket 1,n \rrbracket,\forall z \in \De, ~z\nabla e_i = -\sum_{j=1}^n b_{i,j}(z) e_j$.
\end{center}
\end{mydef}


The following theorem is what we were aiming for.


\begin{mytheo} \label{regular_connections_monodromy}
Two regular systems on $\De$ are equivalent if, and only if, their monodromy is conjugated.
\end{mytheo}

\begin{mydemo}
.
\end{mydemo}

Stated like that, it is not as precise as we would have wanted for a equivalence of categories like in \ref{Holomorphic version on a complex manifold}. The next paragraph will make it more accurate, based on the theorem above.

\medskip
First, a result on the good behavior of algebraic construction (see \ref{algebraic_construction_connection}) with regularity :


\begin{myprop}[\cite{HTT_dmodules}, Proposition 5.1.11] \label{algebraic_regular_connection}
Let $M$ and $N$ be regular meromorphic connections.\\
Then $\Hom_K(M,N)$ and $M \tensor{K} N$ are regular.
\end{myprop}

\begin{mydemo}
.
\end{mydemo}












%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%ù

\paragraph{The local lifting}


This paragraph is partially inspired by [\cite{szamuely_galois}, §2.7] and [\cite{HTT_dmodules}, Lemma 5.2.19] for the lifting of morphisms.\\
The precise Riemann-Hilbert correspondence will be stated next paragraph, based on what we already did in the holomorphic case. In this one, we try to construct a unique (regular) meromorphic connection on $\De$ given a holomorphic connection on $\De^*$.\\
We return to the language of sheaves. Indeed, according to a general fact on non-compact Riemann surfaces, a locally free $\holo_{\De^*}$-module on $\De$ is actually free (for example, see [\cite{forster_riemann}, Theorem 30.4]).
We will denote by $\holo_{\De}(*0)$ the sheaf of meromorphic functions on $\De$ with a pole at $z=0$.


\begin{myprop} \label{local_lifting_sheaf}
Let $(\erond,\nabla)$ a holomorphic connection on $\De^*$.\\
There exists regular meromorphic connection $(\bar{\erond},\bar{\nabla})$ on $\De$ which agrees with $(\erond,\nabla)$ on $\De$. This connection is unique up to isomorphisms (of meromorphic connections).
\end{myprop}

\begin{mydemo}
We can assume $\erond = \holo_{\De}^r$ and $\nabla = d - Adz$. Set $S(z)$ a fundamental system of solutions. Let $C$ the monodromy matrix associated to $\nabla$, $S(z)$ a fundamental system of solutions, and let $B$ a matrix such that $C = \exp(2i\pi B)$. We consider the connection $\bar{\nabla} = d - \frac{B}{z}dz$. A fundamental system of solutions is given by $z^B = e^{B\log(z)}$.\\
Let $U(z) = S(z)z^{-B}$. Then 
\begin{center}
$U(ze^{2i\pi}) = S(ze^{2i\pi})e^{-B\log(ze^{2i\pi})} = S(z)C e^{-2i\pi B}z^{-B} = U(z)$.
\end{center}
Here, by an abuse of notation, $z e^{2i\pi}$ denotes the composition by the simple loop going around 0 counter-clockwise.\\
Therefore, $U(z)$ is single-valued, and then holomorphic on $\De^*$. Its inverse is too, so it defines a isomorphism between $(\erond,\nabla)$ and $(\holo_{\De}(*0)^r,\bar{\nabla}$).

\smallskip
Uniqueness comes from \ref{regular_connections_monodromy}.
\end{mydemo}


To make a functorial statement, we need additionally an extension of morphisms, we will directly do it for the global framework.














%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Global study via patching}

We will state the "meromorphic" Riemann-Hilbert on $\mathbb{P}^1_\CC$ minus a finite set of points. We firstly introduce some global notation compared with what we did the last two paragraphs, and then state and proof the result.\\
Some ideas comes from \cite{szamuely_galois}.

\medskip
In this paragraph, we set $X = \mathbb{P}^1_\CC$, $D = \{s_1,\dots,s_k\} \subset X$ and $Y = X \setminus D$.\\
We denote by $\holo_X(*D)$ the sheaf of meromorphic functions on $X$ with poles along $D$.


\begin{mydef}
Let $\bar{\erond}$ a locally free $\holo_X(*D)$-modules.\\
A \textit{meromorphic connection} on $\bar{\erond}$ is a $\CC$-linear map $\bar{\nabla}:\bar{\erond} \to \bar{\erond} \tensor{\holo_X(*D)} \Omega^1_X$ satisfying the Liebniz rule.
\end{mydef}


\begin{mydef}
We define the category $\locfree^{\bar{\nabla}}(X,D)$ with
\begin{itemize}
\item locally free $\holo_X(*D)$-modules equipped with a meromorphic (flat) connection as objects,
\item morphisms of $\holo_X(*D)$-modules commuting with the connections as morphisms.
\end{itemize}
\end{mydef}


\begin{mytheo} \label{global_lifting_sheaf}
Let $(\erond,\nabla)$ a holomorphic connection on $Y$.\\
There exists regular meromorphic connection $(\bar{\erond},\bar{\nabla})$ on $X$ which agrees with $(\erond,\nabla)$ on $\De$. This connection is unique up to isomorphisms (of meromorphic connections).
\end{mytheo}


\begin{mydemo}
Let $D_i$ small disks around each $s_i$ that do not meet. On each $D_i$, let $(\bar{\erond}_i,\bar{\nabla}_i)$ the unique (up to isomorphisms) lifting of $(\erond_i,\nabla_i) := (\erond,\nabla)|_{D_i}$ given by \ref{local_lifting_sheaf}. On an open set $U$ containing the complementary of $\bigcup_{i=1}^k D_i$ that does not meet $S$, we set $\bar{\erond} = \erond$.\\
 Then, we can glue back the sheaves on $X = \bigcup_{i=1}^k D_i \cup U$ by \ref{patching_sheaf} (the isomorphisms $\theta_{i,j}$ are just given by the ones coming from the construction of the $\bar{\erond}_i$, and the triple intersection condition is empty), which gives us the sheaf $\bar{\erond}$ on $X$ that agrees with $\erond$ on $Y$.
\end{mydemo}


Now, we deal with morphisms :

\begin{myprop}[\cite{HTT_dmodules}, Lemma 5.2.19]
Let $\phi: (\erond_1,\nabla_1) \to (\erond_2,\nabla_2)$ a morphism between holomorphic connections on $Y$.\\
Then, there exists a morphism of meromorphic connections $\bar{\phi} : (\bar{\erond}_1,\bar{\nabla}_1) \to (\bar{\erond}_2,\bar{\nabla}_2)$ on $X$ that restricts to $\phi$.
\end{myprop}


We need two intermediate result.\\

\begin{mylemme}
The restriction map given by \ref{global_lifting_sheaf} induces a bijection :
\begin{center}
$\Gamma(X, \Ker(\bar{\nabla})) \overset{\sim}{\longrightarrow} \Gamma(Y,\Ker(\nabla))$.
\end{center}
\end{mylemme}

\begin{mydemo}
The injectivity is clear. For the surjectivity, let $s \in \Gamma(Y,\Ker(\nabla))$. $\bar{\nabla}$ is regular, so $s$, a solution of the differential equation induced is single-valued as being defined on the whole of $Y$, and therefore has moderate growth - meaning that it can be extended to a meromorphic section on $D$. This concludes.
\end{mydemo}


This one follows the definition.

\begin{mylemme}
Let $(\bar{\erond}_1,\bar{\nabla}_1)$ and $(\bar{\erond}_2,\bar{\nabla}_2)$ two connections on $\De$.\\
Then,
\begin{center}
$\Gamma(X,\connHom_{\holo_{X}(*D)}(\bar{\erond}_1,\bar{\erond}_2)^\nabla) \simeq \Hom_{\locfree^{\bar{\nabla}}(X,D)}((\bar{\erond}_1,\bar{\nabla}_1),(\bar{\erond}_2,\bar{\nabla}_2))$,
\end{center}
where the $\nabla$ on the left-hand side is the one associated to the sheaf $\connHom$ (see \ref{algebraic_construction_connection}).
\end{mylemme}


\begin{mydemo}[\ref{lifting_sheaf}]
Set $\erond = \connHom_{\holo_Y}(\erond_1,\erond_2)$ and $\bar{\erond} = \connHom_{\holo_{X}(*S)}(\bar{\erond}_1,\bar{\erond}_2)$ with the associate $\nabla$ and $\bar{\nabla}$. By \ref{algebraic_regular_connection}, $\bar{\erond}$ is regular, so we can apply the first lemma. The second one thus gives a bijection :
\begin{center}
$\Hom((\bar{\erond}_1,\bar{\nabla}_1),(\bar{\erond}_2,\bar{\nabla}_2)) \simeq \Hom((\erond_1,\nabla_1),(\erond_2,\nabla_2))$,
\end{center}
the surjectivity of which ensures the result.
\end{mydemo}




\begin{mytheo}
The restriction functor 
\begin{center}
$\locfree^{\bar{\nabla}}(X,D) \to \locfree^{\nabla}(Y)$
\end{center}
induces an equivalence of categories.
\end{mytheo}

\begin{mydemo}
The pseudo-inverse functor is given by the construction above, and all the other verifications are clear.
\end{mydemo}


With the work done the previous subsection, we have the correspondence as wished :


\begin{mycoro}[Riemann-Hilbert correspondence, meromorphic case, dimension 1]
There is an equivalence of categories :
\begin{center}
$\locfree^{\bar{\nabla}}(X,D) \cong \locsys(Y)$.
\end{center}
\end{mycoro}




\subsubsection{Sketch of a proof in higher dimension}

bla